### 2019-03-26 README.Rmd
to_rankings

```{r , include = FALSE}

```

@@

The package is under development, so be patient and have fun! We appreciate that issues to be reported in our issues section on Github.

>>>>

@@

The package is under development, so be patient and have fun! If you find any issue, please report it in our [issues section](https://github.com/kauedesousa/gosset/issues).

Use `devtools::install_github` to install the package

```
library("devtools")
install_github("kauedesousa/gosset", upgrade = "never")
```
